A Switching Planner for Combined Task and Observation Planning

### 2010-11-20 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/moritz_2011.tex
Still working on a vocabulary that I am happy with..
 - Charles

\noindent The interpretation of such an expression can be given
according to a recursive descent. Here, an atom is visited as soon as
its conjunctive parent is visited, and a conjunctive term is visited
if all its immediate subterms are visited. A probabilistic term is
visited if exactly one of its subterms, $T_i$, is visited. Each valid
visitation of the root term according to this recursive definition
encapsulates a starting state, along with the probability it
occurs. The former corresponds to the union of all visited atoms, and
the latter corresponds to the product of $p_i$ entries on the visited
subterms of probabilistic elements. Making these ideas concrete, our
example yields the following flat state distribution:

@@

\section{Sequential Planning in POMDP Determinisations}

@@

>>>>

\noindent The interpretation of such an expression can be given
according to a recursive note of {\em visiting} terms. Here, an atom
is visited if its conjunctive parent is visited, and a conjunctive
term is visited if all its immediate subterms are visited. A
probabilistic term is visited if exactly one of its subterms, $T_i$,
is visited. Each valid visitation of the root term according to this
recursive definition encapsulates a starting state, along with the
probability it occurs. The former corresponds to the union of all
visited atoms, and the latter corresponds to the product of $p_i$
entries on the visited subterms of probabilistic elements. Making
these ideas concrete, our example yields the following flat state
distribution:

@@

\section{Switching Planner}

RICHARD, I HAVE STOLEN A FEW LINES FROM YOUR HIPPO THREAD TO SKETCH
THIS STUFF. I HOPE IT'S TAKEN AS FLATTERY :)

We now describe a continual planning approach that switches between
sequential and decision-theoretic planning. The problem at hand is a
POMDP described in DTPDDL.  Our approach uses sequential planning to
compute a linear plan, and one trace of that plan's execution. The
latter encapsulates assumptions about: (1) the true underlying state,
(2) how the plan's execution will progress, and (3) the possibility of
eventually holding strong beliefs about the truth values of specific
state propositions. Sequential planning proceeds in a continual manner
until the validation of an assumption about a runtime state
proposition is scheduled. At that point the system switches to a
decision-theoretic planner that is used to tailor sensory processing
by the robot to test the validity of the assumptions so far.

The problem posed to the decision-theoretic system is an abstraction
of the problem at hand. It is induced according to the executing
sequential plan. Specifically, the abstract process is derived by
first omitting all problem variables that are not mentioned in the
linear trace, and then refining that preliminary model, by
progressively adding more problem variables while the resulting state
space remains sufficiently small. Refinement is a simple and
inexpensive step, guided by the level at which variable symbols occur
in the description of the initial conditions. The abstract process is
also given a utility model that captures the reward (resp. penalty) of
correctly (resp. falsely) in/validating the assumptions made in the
linear trace. In detail, for each assumption on a state variable, we
can have a reward of $1$ for correctly rejecting it, and a penalty of
$-1$ for falsely rejecting it. Decision theoretic planning proceeds in
a more-or-less continual manner until an assumption is rejected, or
until it returns control to the sequential system because it can see
no benefit from performing further actions in the abstraction.

Addressing briefly the specifics of our mobile robot's
architecture. In our scenario the utility model for the POMDP posed to
decision-theoretic planning is sourced from a motivational component
of our robotic architecture. This proposes a non-zero reward
(resp. penalty) for sequential planning with a true (resp. false)
assumption about a state proposition.

\subsection{Sequential Planning in POMDP Determinisations}

@@

\subsection{Abstractions for Decision-Theoretic Planner}
